\documentclass[a4paper,12pt,unpaged]{../comicscript}
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\series{My Daughter, Nova}{1}
\title{Sippy Cup}
\author{Janus Valberg-Madsen}

\begin{document}
\maketitle

\sceneheader{Int.}{Janus' House}{Evening}

\panel[medium-wide shot]
Janus sits by the dinner table with his LAPTOP. 
Nova is standing on the floor next to him, reaching for the DRINKING BOTTLE that Janus is handing to her.
\begin{lettering}
    \dialogue{Nova}{\emph{Me want water!}}
    \dialogue{Janus}{Alright, here you go. Please don't pour it this time.}
\end{lettering}

\panel[medium-close shot]
\label{panel:drinking}
Nova drinks from the bottle with her back turned towards Janus, who is facing away in this shot.
\begin{lettering}
    \sfx{Sip, sip}
\end{lettering}

\panel[identical to \ref{panel:drinking}]
Nova stops drinking and side-eyes towards Janus mischievously.

\panel[wide shot]
\label{panel:pouring}
Nova starts slightly turning the bottle upside down, looking concentrated on what she’s doing. 
Janus is still looking at his laptop, but aware of what’s happening. 
We see Janus’ face in the foreground, in shade, eyes looking down.
\begin{lettering}
    \dialogue{Janus}{Nova. Do \emph{not}. Pour. The water.}
\end{lettering}

\panel[identical to \ref{panel:pouring}]
Nova keeps turning the bottle around, getting a mischievous look on her face.
Janus turns his head slightly, looking suspiciously towards her.

\panel[wide shot]
Janus is running chasingly after Nova, who’s running away while pouring water out wildly. 
Nova has a look of intentional mischief on her face, and Janus looks pissed. 
Speed lines in the background.

\begin{layout}
    \boxpanel{0}{0}{1}{1}{Panel 1}
    \boxpanel{0}{1}{1}{1}{Panel 2}
    \boxpanel{1}{0}{1}{1}{Panel 3}
    \boxpanel{1}{1}{1}{1}{Panel 4}
    \boxpanel{2}{0}{1}{1}{Panel 5}
    \boxpanel{2}{1}{1}{1}{Panel 6}
\end{layout}

\end{document}
